---
title: "Unseen Studies Model"
author: "Hugh Benjamin Zachariae"
date: "April 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Josh's model

Multibinomial model
k = observed studies ~ dbinom(q, N)
N = Total studies ~ multinom(n, A)
n = conjugate prior to N ~ dirichlet()
q = probability for publication <- R + p(1-R)
R = probability for significant results ~ dbeta(.5, .5)
rho = rate of unsignificant publications ~ dunif(0,1) (maybe set 0.1, 0.5 and 0.9)


Article:

N-k ~ dnbinom(k, q)
  = number failures it takes until we see k successes (finding a study) with Q probability.
Q ~ dbeta(0.5, 0.5)
  = accounting for variability of prob of publication across fields.
  = R + rho(1-R): Assuming all significant studies are published and some proportion 0 <= rho <= 1 of non-significant studies are published. 
R
  = prob of producing significant results.
Z ~ dbinom(k, r)
  = r = z/k


  
  
We need to assume that studies are of roughly the same sample size to have the same R across studies as larger power increases likelihood of significant results.

  
```{r}
plot(dnbinom(seq(1,10), 7, 0.5))
```


